JSSET: JavaScript Semantics Extraction Toolchain

### 2019-08-15 icse/parser.tex
Written abstract

\subsubsection{Parser generations}\label{sec:convert-bnfes}
The next step is to automatically extract parsers from the given \( \bnfes \) grammar.
The conversion from \( \bnfes \) symbols into Scala codes is defined as follows:
\[
  \begin{array}{c|c}
    \bnfes \; \text{symbols} & \text{Scala codes}\\\hline\hline
    \epsilon & \code{MATCH}\\\hline
    \T{a} & \code{"a"}\\\hline
    \NT{A}(\argument_1, \argument_n) & \code{A(a1, .. , an)}\\\hline
    \symb? & \code{opt(s)}\\\hline
    \symb \butnot \symb' & \code{s\textbackslash s'}\\\hline
    \nolt & \code{NoLineTerminator}\\\hline
  \end{array}
\]
The \( \code{MATCH} \) denotes the empty sequence of lookahead parsers.
Each String literals are implicitly converted into lookahead parsers
through Scala implicit conversions. The \( \code{opt(s)} \) funciton
is same with \( \code{s | MATCH} \). We also define \( \code{\textbackslash} \)
opertor between parsers to support exclusive parsers.
Finally, we support the \( \code{NoLineTerminator} \) parser.
It is a little bit tricky because it should hook the whitespace parsers
and check whether it contains line terminators.
However, it is possible in our approach because
we also automatically generates lexers not only parsers of ECMAScript syntax.
For the final result, the automatically synthesized parser from the
production \( ArrayLiteral \) in Figure~\ref{fig:array-literal} is defined
as the parsers defined in Figure~\ref{fig:array-literal}.

Moreover, we support automatic semicolon insertion algorihtms as well.
It is the most distinctive parsing feautres in ECMAScript to parse more programs.
We extend our parser implementation to keep track of the right-most position
that fails to be parsed in the given input. In ECMAScript, the token at that
position is defined as \textit{offending token} and automatic semicolon insertion
algorithms are defined with such tokens. The algorithm is quite easy when we
already have the position offending tokens, because there are only three simple
rules. Thus, we just manually support them by following the rule in ECMAScript 2019.
Moreover, the rule is rarely changed because the only one sub-rule is added
after ECMAScript 5.1 written in 2011.

>>>>

\subsubsection{Parser generations}\label{sec:convert-bnfes}
The next step is to automatically extract parsers from the given \( \bnfes \) grammar.
The conversion from \( \bnfes \) symbols into Scala codes is defined as follows:
\[
  \begin{array}{c|c}
    \bnfes \; \text{symbols} & \text{Scala codes}\\\hline\hline
    \epsilon & \code{MATCH}\\\hline
    \T{a} & \code{"a"}\\\hline
    \NT{A}(\argument_1, \argument_n) & \code{A(a1, .. , an)}\\\hline
    \symb? & \code{opt(s)}\\\hline
    \symb \butnot \symb' & \code{s\textbackslash s'}\\\hline
    \nolt & \code{NoLineTerminator}\\\hline
  \end{array}
\]
The \( \code{MATCH} \) denotes the empty sequence of lookahead parsers.
Each String literals are implicitly converted into lookahead parsers
through Scala implicit conversions. The \( \code{opt(s)} \) function
is same with \( \code{s | MATCH} \). We also define \( \code{\textbackslash} \)
operator between parsers to support exclusive parsers.
Finally, we support the \( \code{NoLineTerminator} \) parser.
It is a little bit tricky because it should hook the white space parsers
and check whether it contains line terminators.
However, it is possible in our approach because
we also automatically generates lexers not only parsers of ECMAScript syntax.
For the final result, the automatically synthesized parser from the
production \( ArrayLiteral \) in Figure~\ref{fig:array-literal} is defined
as the parsers defined in Figure~\ref{fig:array-literal}.

Moreover, we support automatic semicolon insertion algorithms as well.
It is the most distinctive parsing features in ECMAScript to parse more programs.
We extend our parser implementation to keep track of the right-most position
that fails to be parsed in the given input. In ECMAScript, the token at that
position is defined as \textit{offending token} and automatic semicolon insertion
algorithms are defined with such tokens. The algorithm is quite easy when we
already have the position offending tokens, because there are only three simple
rules. Thus, we just manually support them by following the rule in ECMAScript 2019.
Moreover, the rule is rarely changed because the only one sub-rule is added
after ECMAScript 5.1 written in 2011.

### 2019-08-15 icse/related.tex
More writing for algorithm compiler
Written abstract

\subsection{Automatic Model Generation}
There is similiar problems in many fields. Not only langauge semantics, many specification is not constructed formally, so many researcheres are trying to
extract formal semantics of target specification. To reduce manual efforts to get models of target system, there are few studies about automatic generation of
formal semantics from specification. \cite{javadoc} is closely related work of ours, which uses javadoc comments of target API function with NLP techniques and various
heuristic methods, to generate java code which correctly models target. They produces several candidate codes, and test their codes with actual implementation of API functions
to find correct modeling. Unlike their approaches, we provides specification translation assistant to support future language update, and to provide correct meaning of specification, which also can applicable when
testing for each primitive is unavailable so we cannot decide correct semantics automatically.

@@

\subsection{Formal Semantics of JavaScript}
Building formal semantics of language is important for program verification and static analysis. JavaScript is most widely-used language in
web browser, but its complex behavior makes confusion to developer and program analysis designer. So there are many reseraches to define formal semantics of JavaScript and
using it to formal verification or program analysis. \cite{lambdajs} define the core calculus of JavaScript, and express rest of the features as desugraing. Their method can
work for subset of JavaScript, but their formalization is not directly mapped to specification document. So it requires deep understanding of current and upcoming specification,
which needs lots of effort. \cite{kjs} and \cite{javert} defines formal semantics of JavaSciprt based on ECMAScript specification, and they manually convert from specification
to formal languages. KJS mapped from ECMAScript 5 specification to K framework, which can be used in program verifiaction and analysis. Similarly, JaVerT coverts specification
to their own language (called JSIL) to make further analysis. Compared to these approaches, we suggests to generate converter from specification to intermediate language, with
convertion assistant and layered translation technique to minimize human effort and to apply for further update or even unconfirmed proposal of specification.

>>>>

\subsection{Automatic Model Generation}
There is similar problems in many fields. Not only language semantics, many specification is not constructed formally, so many researches are trying to
extract formal semantics of target specification. To reduce manual efforts to get models of target system, there are few studies about automatic generation of
formal semantics from specification. \cite{javadoc} is closely related work of ours, which uses Javadoc comments of target API function with NLP techniques and various
heuristic methods, to generate java code which correctly models target. They produces several candidate codes, and test their codes with actual implementation of API functions
to find correct modeling. Unlike their approaches, we provides specification translation assistant to support future language update, and to provide correct meaning of specification, which also can applicable when
testing for each primitive is unavailable so we cannot decide correct semantics automatically.

% TODO pseudo code의 형태와 natural language의 결합이다.
% TODO moudular test로 guide를 받을 수 없어서 user defined rule을 사용. 대신, statistical analysis를 기반으로 guide해줌

@@

\subsection{Formal Semantics of JavaScript}
Building formal semantics of language is important for program verification and static analysis. JavaScript is most widely-used language in
web browser, but its complex behavior makes confusion to developer and program analysis designer. So there are many researches to define formal semantics of JavaScript and
using it to formal verification or program analysis. \cite{lambdajs} define the core calculus of JavaScript, and express rest of the features as desugaring. Their method can
work for subset of JavaScript, but their formalization is not directly mapped to specification document. So it requires deep understanding of current and upcoming specification,
which needs lots of effort. \cite{kjs} and \cite{javert} defines formal semantics of JavaScript based on ECMAScript specification, and they manually convert from specification
to formal languages. KJS mapped from ECMAScript 5 specification to K framework, which can be used in program verification and analysis. Similarly, JaVerT coverts specification
to their own language (called JSIL) to make further analysis. Compared to these approaches, we suggests to generate converter from specification to intermediate language, with
conversion assistant and layered translation technique to minimize human effort and to apply for further update or even unconfirmed proposal of specification.
